%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Andrew Ryan}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Brooklyn Technical High School}{Brooklyn, NY}
      {GPA 3.76, Class rank 63/350, SAT 1510}{Sept. 2021 -- Jun 2025}
  \resumeSubHeadingListEnd


%-----------Extracurriculars-----------
\section{Extracurricular Activities}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Student Government}{Sept. 2023 -- Jun. 2024}
      {Treasurer}{Brooklyn, NY}
      \resumeItemListStart
        \resumeItem{Developed budget proposals, collaborating with the student government team to plan major school events.}
        \resumeItem{Organized and led fundraising events, \textbf{raising over \$5,000} for school activities and projects.}
        \resumeItem{Managed the student government budget, ensuring accurate tracking and allocation of funds.}
    
      \resumeItemListEnd
      
    \resumeSubheading
      {Math Team}{Sept. 2022 -- Present}
      {Team Captain}{Brooklyn, NY}
      \resumeItemListStart
        \resumeItem{Competed in regional, state, and national-level math competitions\textbf{(NYCIML, NYCMTS).}}
        \resumeItem{Facilitated weekly study sessions to discuss high-level \textbf{Probability Theory, Geometry \& Algebra.}}
        \resumeItem{Led a 26-member math team as captain, overseeing strategy development and competition preparation.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Varsity Swim Team}{Sep. 2021 -- June 2024}
      {Team Captain}{Brooklyn, NY}
      \resumeItemListStart
        \resumeItem{Led the varsity swim team to its \textbf{inaugural section championship} through leadership and strategic planning.}
        \resumeItem{Mentored junior team members, providing guidance on proper techniques, race preparation, and sportsmanship.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------Experience-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {FlexiDip}{June 2024 -- Present}
      {Co-Founder}{Ann Arbor, MI}
      \resumeItemListStart
        \resumeItem{\textbf{Co-founded startup} specializing in adjustable dipping containers, optimizing buffalo wing dining experience.}
        \resumeItem{Developed minimum viable product(MVP) capable of early-stage revenue generation.}
        \resumeItem{Received positive feedback from established brands like Buffalo Wild Wings for innovative sauce holder designs.}
        \resumeItem{Validated startup idea through market research and interview feedback as a part of Launch-X U-Michigan.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Private Math Tutor}{Sept. 2021 -- Present}
      {Team Captain}{Brooklyn, NY}
      \resumeItemListStart
        \resumeItem{Provided personalized tutoring sessions in algebra, calculus, and geometry to elementary \& middle-school students}
        \resumeItem{Developed lesson plans for diverse learning styles, leading to improvements by \textbf{upwards of 1.5 letter grades}.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd


\section{Awards}
    \resumeSubHeadingListStart
      \resumeSubheading
      {Speedo Scholastic All-American}{Aug. 2023 -- Present}
      {}{}
      \resumeItemListStart
      \vspace{-4mm}
        \resumeItem{National award given to student-athletes who achieve a \textbf{national time standard }while maintaining a 3.5+ GPA.}
      \resumeItemListEnd
      
    \resumeSubheading
      {National Junior Honor Society}{June 2023 -- Present}
      {}{}
      \resumeItemListStart
      \vspace{-4mm}
        \resumeItem{Award presented to students with outstanding achievements in academics, leadership, and community service.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------Courses-----------
\section{Classes}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \vspace{1mm}
     \textbf{Courses}{: AP Calulus BC, AP Chemistry, AP Physics, AP World History, AP U.S. History, AP Statistics, AP Literature} \\

    }}
 \end{itemize}

%-----------Skill and Interests-----------
\section{Skills \& Interests}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \vspace{1mm}
     \textbf{Skills}{: Probability Theory, Web Design, Microsoft Excel, Microsoft Office} \\
     \vspace{1mm}
     \textbf{Interests}{: Photography, Creative Writing, Archery, New York Knicks} \\
     \vspace{1mm}

    }}
 \end{itemize}
 \begin{center}
    
\small 123-456-7890 $|$
\href{mailto:ADD EMAIL HERE@x.com}{\underline{andrew@gmail.com}} $|$
\href{ADD LINKEDIN PAGE HERE}{\underline{linkedin.com/in/andrew}} 
\end{center}


\end{document}